Supplementary methods

### 2020-08-25 text/supplemental_methods.Rmd
Fix placement of SM2 in supp meths

### Survival
```{r child='../code/figureSM2.Rmd'}
```

**supplementary figure SM2** gives a comparison between the post-fit
survival curves for men and women vs the CDC data it is based on. This
comparison does not distinguish on ethnicity for simplicity in
visualization.

@@

@@

**SM2 Legend here**

>>>>

**Supplementary figure SM2** gives a comparison between the post-fit
survival curves for men and women vs the CDC data it is based on. This
comparison does not distinguish on ethnicity for simplicity in
visualization.

@@

#### Figure SM2

@@

**Supplementary Figure SM2** Comparison between CDC data and ODE model fit for
males and females of European descent.
